paper_replication

### 2021-12-13 paper_replication.Rmd
Update paper_replication.Rmd

BIG PROBLEM: data on abortion restrictions starts at the end of December 2018, but data on abortion counts only goes up to (max) 2018
   * Option 1: Somehow find abortion restriction data from before December 2018 - I tried with no luck yet
   * Option 2: Somehow find abortion count data for 2019 on - Also tried with no luck yet 
         - I found this by state but not by county.

@@

TODO: Calculate distances to nearest clinic
    - I added 'county_pop_centroids.csv' from the Census Bureau
    - In the paper they did centroid of county of residence centroid of nearest county  with a clinic, but I think because we have the lat and long in the provider list we can do centroid of county of residence to nearest clinic

TODO: Calculate abortion rates by county

@@

```{r, echo=FALSE, message=FALSE, warning=FALSE}
provider_list_geo <- read.csv('data/provider_list_geo.csv')

```

@@

>>>>

@@

@@

```{r, echo=FALSE, message=FALSE, warning=FALSE}
provider_list_geo <- read.csv('data/provider_list_geo.csv')
```

@@

Data on the county-level voting totals came from the Harvard Dataverse.
Available at https://dataverse.harvard.edu/dataset.xhtml?persistentId=doi:10.7910/DVN/VOQCHQ. Accessed 12/13/21.
